WDIAS : A Microservices-Based Weather Data Integration and Assimilation System\\

### 2020-04-26 method/sec_3-microservice.tex
v5.0

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{\acrshort{wdias} Microservices}
\label{sebse:wdias_microservices}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{\acrshort{wdias} \acrfull{api}}
\label{sebse:wdias_api}

@@

Other than the above endpoints, we exposed another set of endpoints to configure extensions, and we will describe further in \cref{se:data_preprocess}.
Other than the timeseries metadata, as mentioned in the list of endpoints, other module endpoints start with the module name such as import, export, and extension. Using the above convention, we allowed adding a new module system if required.
For import and export modules, the names of the endpoints defined as the modules name then follow the data format. The above endpoint naming convention provides the flexibility to integrate new data format modules for import and export. Then the endpoint name ends with the type of data operation. Data can upload as a single file with binary or multiple files with the upload. Other than that, users can send requests with raw data with required headers has mentioned by a particular import module.
Thus the \acrshort{api} convention of \texttt{\hl{/MODULE/DATA\_FORMAT/DATA\_TYPE}} allows users to integrate new import or export modules into the system as well as add new data types.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{WDIAS Microservices}
\label{sebse:wdias_microservices}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{WDIAS Application Programming Interface}
\label{sebse:wdias_api}

@@

Other than the above endpoints, we exposed another set of endpoints to configure extensions, and we will describe further in \cref{se:data_preprocess}.
Other than the timeseries metadata endpoints, other module endpoints start with the module name such as import, export, and extension when compared to timeseries metadata endpoints. Using the above convention, we allowed adding a new module system if required.
For import and export modules, the names of the endpoints defined as the modules name then follow the data format. The above endpoint naming convention provides the flexibility to integrate new data format modules for import and export. Then the endpoint name ends with the type of data operation. Data can upload as a single file with binary or multiple files with the upload. Other than that, users can send requests with raw data with required headers has mentioned by a particular import module.
Thus the \acrshort{api} convention of \texttt{/MODULE/DATA\_FORMAT/DATA\_TYPE} allows users to integrate new import or export modules into the system as well as add new data types.

### 2020-04-26 method/sec_5-data_preprocess.tex
v5.0

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.5\textwidth]{method/data_preprocess/weather_data_preprocessing.jpg}
    \caption{\hl{Weather data preprocessing using a generic mathematical function model}}
    \label{fi:weather_data_preprocessing}
\end{figure}

@@

\subsection{Transformation}- Simple arithmetic manipulation, Time interval transformation and Shifting the series in time Specific hydro-meteorological transformation such as stage discharge relationships.
\begin{figure}[htp]
    \centering
    \includegraphics[width=0.6\textwidth]{method/data_preprocess/transformation.jpg}
    \caption{\hl{Time interval transformation.}}
    \label{fi:transformation}
\end{figure}

\subsection{Validation}- Checks for counting reliable, doubtful, unreliable, and missing values
\begin{figure}[htp]
    \centering
    \includegraphics[width=0.6\textwidth]{method/data_preprocess/validation.jpg}
    \caption{\hl{Timeseries data validation against a set of rules.}}
    \label{fi:validation}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Extension \acrfull{api} for Data Prepossessing}

>>>>

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.5\textwidth]{method/data_preprocess/weather_data_preprocessing.jpg}
    \caption{A generic mathematical function model for weather data preprocessing}
    \label{fi:weather_data_preprocessing}
\end{figure}

@@

\subsection{Transformation}
Simple arithmetic manipulation, Time interval transformation and Shifting the series in time Specific hydro-meteorological transformation such as stage discharge relationships.
\begin{figure}[htp]
    \centering
    \includegraphics[width=0.6\textwidth]{method/data_preprocess/transformation.jpg}
    \caption{Time interval aggregration.}
    \label{fi:transformation}
\end{figure}

\subsection{Validation}
Checks for counting reliable, doubtful, unreliable, and missing values
\begin{figure}[htp]
    \centering
    \includegraphics[width=0.6\textwidth]{method/data_preprocess/validation.jpg}
    \caption{Timeseries data validation.}
    \label{fi:validation}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Extension API for Data Prepossessing}
